Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-02-05 paper/arm.tex
hacking at address dependencies
Working on appendices

\begin{definition}
  \label{def:DS}
  % Let $[\FALSE/\D]$ be the substitution that performs $[\FALSE/\Dx{\aLoc}]$
  % for every $\aLoc$.
  Let $[\aForm/\Dx{*}]$ substitute $\aForm$ for every $\Dx{\bLoc}$.\\
  Let formula $\DL{\aLoc}{\amode}$ and substitution $\DS{\aLoc}{\amode}$ be defined:
  \begin{align*}
    \DL{\aLoc}{\mRLX}&=\TRUE
    &\DS{\aLoc}{\mRLX}&=[\TRUE/\Dx{\aLoc}] 
    \\
    \DL{\aLoc}{\mRA}&=\Dx{\aLoc}%\land\D{}
    &\DS{\aLoc}{\mRA}&=[\FALSE/\D]
    \\
    \DL{\aLoc}{\mSC}&=\Dx{\aLoc}%\land\D{}
    &\DS{\aLoc}{\mSC}&=[\FALSE/\D]
  \end{align*}
\end{definition}
\begin{definition}[\xCO/\xRASC/\xDGR]
  \label{def:pomsets-down}
  Update \refdef{def:pomsets-ra} to (\ref{L4} unchanged):
  \begin{enumerate}
  \item[\ref{S4})]
    $\aTr{\bEvs}{\bForm}$ implies
    \begin{math}
      \bForm
      \DS{\aLoc}{\amode}
      [(\Qw{\aLoc}\land\aExp{=}\aVal)/\Qw{\aLoc}],
    \end{math}
  \item[\ref{S5})]
    $\aTr{\cEvs}{\bForm}$ implies
    \begin{math}
      \bForm
      \DS{\aLoc}{\amode}
      [\FALSE/\QS{\aLoc}{\amode}],
    \end{math}
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies
    \begin{math}
      \aVal{=}\aReg\limplies\bForm,
    \end{math}
  \item[\ref{L5})]
    $\aTr{\cEvs}{\bForm}$ implies
    \begin{math}
      \DL{\aLoc}{\amode}\land \bForm[\FALSE/\QL{\aLoc}{\amode}].
    \end{math}
  \end{enumerate}
\end{definition}
Load actions that require downgrading introduce $\Dx{\aLoc}$.
Relaxed stores on $\aLoc$ substitute true for $\Dx{\aLoc}$, whereas
synchronizing stores substitute false for $\Dx{\aLoc}$.

@@

\begin{definition}[\xRRD]
  \label{def:pomsets-rr}
  Update \refdef{def:pomsets-trans} to:
  \begin{enumerate}
  \item[\ref{T3})]
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\TRUE/\RW]$ if $\labelingAct_1(\aEv)$ is a write,
    \\
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\FALSE/\RW]$ otherwise.
  \end{enumerate}
  \begin{enumerate}
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies $\aVal{=}\aReg\limplies\bForm$, 
  \item[\ref{L5})]
    % $\aTr{\cEvs}{\bForm}$ implies $\RW\limplies(\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm$,
    $\aTr{\cEvs}{\bForm}$ implies $(\aVal{=}\aReg\lor\RW)\limplies\bForm$,
  \end{enumerate}  
\end{definition}
\ref{L5} requires $\aTr{\cEvs}{\bForm}$ implies $\bForm$ for writes and
$\aTr{\bEvs}{\bForm}$ implies $\aVal{=}\aReg\limplies\bForm$ for reads.  For
reads, the dependent and independent predicate transformers are identical.

>>>>

\begin{definition}
  \label{def:DS}
  % Let $[\FALSE/\D]$ be the substitution that performs $[\FALSE/\Dx{\aLoc}]$
  % for every $\aLoc$.
  Let $[\aForm/\Dx{*}]$ substitute $\aForm$ for every $\Dx{\bLoc}$.\\
  Let formula $\DL{\aLoc}{\amode}$ and substitution $\DS{\aLoc}{\amode}$ be defined:
  \begin{align*}
    \DL{\aLoc}{\mRLX}&=\TRUE
    &\DS{\aLoc}{\mRLX}&=[\TRUE/\Dx{\aLoc}] 
    \\
    \DL{\aLoc}{\mRA}&=\Dx{\aLoc}%\land\D{}
    &\DS{\aLoc}{\mRA}&=[\FALSE/\D]
    \\
    \DL{\aLoc}{\mSC}&=\Dx{\aLoc}%\land\D{}
    &\DS{\aLoc}{\mSC}&=[\FALSE/\D]
  \end{align*}
\end{definition}
\begin{definition}[\xCO/\xRASC/\xDGR]
  \label{def:pomsets-down}
  Update \refdef{def:pomsets-ra} to: % (\ref{L4} unchanged):
  \begin{enumerate}
  \item[\ref{S4})]
    $\aTr{\bEvs}{\bForm}$ implies
    \begin{math}
      \bForm
      \DS{\aLoc}{\amode}
      [(\Qw{\aLoc}\land\aExp{=}\aVal)/\Qw{\aLoc}],
    \end{math}
  \item[\ref{S5})]
    $\aTr{\cEvs}{\bForm}$ implies
    \begin{math}
      \bForm
      \DS{\aLoc}{\amode}
      [\FALSE/\QS{\aLoc}{\amode}],
    \end{math}
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies
    \begin{math}
      \aVal{=}\aReg\limplies\bForm,
    \end{math}
  \item[\ref{L5})]
    $\aTr{\cEvs}{\bForm}$ implies
    \begin{math}
      \DL{\aLoc}{\amode}\land \bForm[\FALSE/\QL{\aLoc}{\amode}].
    \end{math}
  \end{enumerate}
\end{definition}
Load actions that require downgrading introduce $\Dx{\aLoc}$.
Relaxed stores on $\aLoc$ substitute true for $\Dx{\aLoc}$, whereas
synchronizing stores substitute false for $\Dx{\aLoc}$.

@@

\begin{definition}[\xRRD]
  \label{def:pomsets-rr}
  Update \refdef{def:pomsets-trans} to:
  \begin{enumerate}
  \item[\ref{T3})]
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\TRUE/\RW]$ if $\labelingAct_1(\aEv)$ is a write,
    \\
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\FALSE/\RW]$ otherwise.
  \end{enumerate}
  \begin{enumerate}
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies $\aVal{=}\aReg\limplies\bForm$, 
  \item[\ref{L5})]
    % $\aTr{\cEvs}{\bForm}$ implies $\RW\limplies(\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm$,
    $\aTr{\cEvs}{\bForm}$ implies $(\aVal{=}\aReg\lor\RW)\limplies\bForm$,
  \end{enumerate}  
\end{definition}
For reads, the dependent and independent predicate transformers are identical
(since $\RW$ is $\FALSE$).  For writes, \ref{L5} requires
$\aTr{\cEvs}{\bForm}$ implies $\bForm$ for the independent case (since $\RW$
is $\TRUE$).
